Navigating to a greener Europe with 24/7 hourly clean electricity procurement

### 2023-10-03 manuscript/sections/introduction.tex
intro: outline section

\textbf{Dummy abstract from ECEMP - to refine}

Climate change is driving a global effort to rapidly decarbonise electricity systems across the globe. 
Many public and private energy buyers have joined this effort and highlight their sustainable credentials by procuring renewable energy with the Power Purchase Agreements (\gls{ppa}s).
\gls{ppa}s typically allow for renewable energy to match supply and demand on average over a long period of time. 
For example, more than 360 members of the there100.org group\footnote{\url{https://www.there100.org/}} have committed to purchasing enough renewable energy to match 100\% of their electricity consumption on an annual basis. 
Such voluntary commitments accelerate the deployment of wind and solar capacity above the policy requirements in the countries and jurisdictions these companies operate.

However, the energy buyers that commit to 100\% annual matching from Renewable Energy Sources (\gls{res}) still face times when generation from wind and solar generators is not sufficient to match the companies' electricity demand.
During those hours, the energy buyers often have to rely on carbon-emitting power generating technologies available on the local market, such as coal and gas. 
The energy demand supplied by the annual matching approach is thus not \textit{entirely} carbon-free. 
Furthermore, 100\% annual matching approach keeps electricity buyers exposed to price volatility. 
Finally, it requires the energy system to maintain backup and flexibility options for hours with low renewable generation.

For this reason, there is growing interest from corporations such as Google to match their demand with clean energy supply on a truly 24/7 basis. 
Achieving 24/7 Carbon-Free Energy (CFE) means that every kilowatt-hour of electricity consumption is met with carbon-free electricity sources, every hour of every day. 
Thus, this approach has the potential to eliminate all carbon emissions associated with Google's electricity use completely. 
In 2020 Google committed to the ambitious goal of operating entirely on a 24/7-CFE approach at all its data centres and campuses worldwide by 2030 \cite{Google-1}. 
Shortly after, Google published a policy roadmap on achieving the 24/7-CFE goal \cite{Google-2}.

@@

>>>>

% Introduction Structure

% 1. **Opening & Introduce the global momentum towards renewable energy adoption.**

Climate change is driving a global effort to rapidly decarbonise electricity systems across the globe. 
The European Union (\gls{eu}) has committed to achieve net-zero emissions by 2050, and the European Commission has adopted the European Climate Law with a target of reducing net greenhouse gas emissions by at least 55\% by 2030, compared to 1990 levels \cite{EuropeanClimateLaw2020}. 
National climate initiatives span the globe, including the United States with the Biden administration's goal of reducing emissions by 50-52\% by 2030, compared to 2005 levels \cite{BidenClimatePlan2021}, and China's commitment to "have \co emissions peak before 2030 and achieve carbon neutrality before 2060” \cite{ChinaNetZero-IEA}.

% 2. **Evolution, approaches and challenges of voluntary clean energy procurement**

Many public and private energy buyers join this effort by purchasing clean energy to demonstrate their sustainability credentials, which, in the best case scenario, can result in additional renewable energy capacity deployment and a reduction in energy buyers' carbon footprints.

The established schemes for voluntary clean energy procurement that have been in use for decades are the Guarantees of Origin (\gls{go}s) in Europe and the Renewable Energy Certificates (also known as Renewable Energy Credits) (\gls{rec}s) in the United States.
A common feature of these schemes is that renewable energy credits are "unbundled" from megawatt-hours of energy and can be traded numerous times on specialized markets before being retired.
The owner gets to claim environmental benefits when "retiring" (i.e. using) the certificate.
The unbundled renewable energy credits, however, have been criticized by researchers and non-governmental organisations (\gls{ngo}s) for not ensuring a physical match between renewable energy generation and consumption, and for absence of evidence that such schemes drive build-out of additional renewable energy capacity \cite{bjorn-RECSnatcom-2022, gillenwater-2014, re100report-2020, spglobal-recs, bock-icelandGOproblem}.

Some corporate and industrial (\gls{ci}) buyers recongnised the problems associated with the unbundled certificates and turned towards Power Purchase Agreements (\gls{ppa}s). 
When signing a \gls{ppa}, energy buyers pledge to buy both the energy and the environmental credits ("bundled") to megawatt-hours.
Market-driven procurement of renewable energy has become one of the major drivers of the energy transition: \gls{ppa}s are expected to account for one-fifth of utility solar PV and wind capacity expansion in 2023--2024, and almost twice as much (36\%) when China is excluded \cite{iea-REppa2023}.
In some countries, such as Spain and Sweden, market-driven procurement of renewable energy capacity has already surpassed policy-driven capacity expansion \cite{iea-REppa2023}.

\textbf{The key problem --} In most cases, \gls{ppa}s enable renewable energy to match supply and demand over a long period of time.
As an example, more than 400 members of the there100.org group\footnote{\url{https://www.there100.org/}} have committed to purchasing renewable energy that matches 100\% of their electricity consumption on an annual basis.
In spite of such ambitious targets, these buyers still face periods when wind and solar generators signed with \gls{ppa}s cannot supply enough electricity to meet their needs.
During those hours, energy buyers often have to depend on carbon-emitting technologies, like coal and gas, available on local markets.
As a result, the 100\% annual renewable matching approach does not entirely eliminate carbon emissions from the energy buyers portfolio.
Furthermore, 100\% annual matching approach keeps electricity buyers exposed to price volatility, as the price of electricity on the wholesale markets can vary significantly from hour to hour.

% 3. **24/7 Carbon-free Energy Procurement**
% Introduce the 24/7 CFE idea
% Initiatives corporate and NGO interest in 24/7 Carbon-free Energy Procurement

\textbf{Proposed solution --} There is growing interest from the leaders in the clean energy procurement to move beyond the 100\% annual matching approach.
The next frontier in the clean energy procurement is the 24/7 Carbon-Free Energy (\gls{cfe}) procurement, which aims to match clean energy supply with electricity demand on an hourly basis.
Thus, 24/7-CFE procurement has the potential to eliminate \textit{all greenhouse gas emissions} associated with electricity use of the parciticpating companies.
Furthermore, 24/7-CFE procurement is focused on \textit{carbon-free} rather than renewable energy, which opens up opportunities for a broad range of advanced energy technologies, such as long-duration energy storage (\gls{ldes}) or new clean firm power generators that are needed for deep decarbonisation of the energy systems.

Google broke the 24/7 ground in 2020 by announcing its commitment to entirely on the 24/7-CFE approach at all its data centres and campuses worldwide by 2030 \cite{google-247by2030}.
Shortly after, Google published a policy roadmap on achieving the goal \cite{google-PolicyRoadmap}.
Also, Microsoft has committed to the 100/100/0 by 2030 goal (i.e. "100\% of electricity consumption, 100\% of the time, matched by zero carbon energy purchases") \cite{Microsoft-vision}. 
The list of entities that have committed to 24/7-CFE procurement includes also utilities, such as Peninsula Clean Energy (a community choice aggregator in California) committed to 24/7~CFE by 2025 \cite{peninsula-OurPathto247}, and even cities like Des Moines, Iowa U.S., with a commitment by 2035 \cite{iowaenvcouncil-247}.

In 2021, an international group of energy suppliers, buyers, and \gls{ngo}s launched the 24/7 Carbon-free Energy Compact.\footnote{\url{https://gocarbonfree247.com/}}
With over 135 signatories, the group aims to "develop and scale high-impact technologies, energy policies, procurement practices, aand solutions to make 24/7 Carbon-Free Energy achievable for all.".

% 5. **24/7 model-based studies review**
\textbf{State of research --}

\cite{chalendar-2019}

% 6. **Relevance of this paper**

@@

% 7. **Prologue**
